\input{config/config.tex}
\usepackage{ulem}

\fancyhead[L]{
Application No.: 13/763,627 \newline 
Reply to office action of March 18, 2014}

\begin{document}
IN THE UNITED STATES PATENT AND TRADEMARK OFFICE

\heading{I. CAPTION}

In re the Application of: PATENT \newline
Applicant: Vladimir Vassilev \newline
Application No.: 13/763,627 \newline
Application Title: Digital aerophones and dynamic impulse response
systems \newline
Examiner: Warren, David S \newline
Art Unit: 2832 \newline


\begingroup
\setlength\parindent{3.6in}
Sverderups gate 1A, 0559 Oslo \\ March 26, 2014
\endgroup

Commissioner for Patents \newline
Post Office Box 1450 \newline
Alexandria, Virginia 22313-1450 \newline

Sir:

\textbf{Remarks} begin on page 2 of this paper.

\newpage
\begin{center}
REMARKS
\end{center}

Claim Rejections - 35 USC  102
Quote from office action of March 18, 2014:

\begin{quote}

Claims 1 - 4 are rejected under pre-AIA 35 U.S.C. 102(b) as being anticipated by
Zinato (2006/0201312). Regarding claims 1 - 4, (as best as can be determined, see
112 rejection supra), Zinato discloses determining the dynamic impulse response (i.e.,
in real time) of an aerophone (human-interaction and playing are inherent in any
musical keyboard instrument). The church organ flue pipes of Zinato are synonymous
with Applicant's aerophone.

\end{quote}



The subject matter of Zinato (2006/0201312) has no content relevant to "determining the dynamic impulse response (i.e., in real time) of an aerophone" as you claim. What is described in Zinato (2006/0201312) is a method for real time synthesis of soundwave based on the \textbf{\underline{static}} impulse response for each one of the church organ flue pipes and dynamic (i.e., in real time) input from electronic keyboard. It is true that organ flue pipes are aerophones but they have static impulse response which does not change as result of player interaction. The current invention focuses on aerophones with dynamic impulse response controlled by the player e.g. bagpipe chanter. In those aerophones the player changes the impulse response of the aerophone by opening and closing holes or changing the dimensions of the acoustic chamber of the aerophone. In fact Zinato (2006/0201312) can be used as a positive argument for the innovative value of the current application. There is no reason he would restrict his soundwave synthesis method to aerophones with static acoustic impulse response if he had knowledge of the method proposed in this application which would allow him to use his method with all aerophones including those with dynamic impulse response. As described in the current applications description the method for synthesizing a soundwave from the player interaction is divided into two parts where the first one is responsible for periodic calculation of the impulse response of the acoustic system of the aerophone. The second uses the output from the first as input. That second part can be as simple as the least sum of squares method described here (see [0033], [0034]) which produces discrete state values (e.g. to be used with MIDI or as key press human interaction events). The other alternative for the second part of the algorithm (see [0035]) is to use the impulse response for convolution with signals in any discrete signal system producing realistic output waveform signal. The method described in Zinato (2006/0201312) is a specific implementation of the second alternative of the second part of the method of synthesis algorithm.

Both Zinato (2006/0201312) and Ryle (2007/0227344) which was referenced in the first office action are disclosing specific implementations of digital signal systems based on FIR filters using predetermined static impulse responses as convolution vectors. None of them are relevant to the subject of the current application which discloses a method of real time estimation of the impulse response and use of those dynamic impulse responses in algorithms synthesizing output signal waveform.


In view of the above, it is submitted that the claims are in a condition for allowance. Reconsideration of the objections and rejections is requested.

\setlength\parindent{3.6in}

Respectfully submitted, \\Vladimir Vassilev

\end{document}
